Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2022-01-28 document/source/body.tex
has have

% NEW TEXT
Determinism is a key requirement for simulation during AV development and testing, it ensures repeated runs have the same output and therefore has zero variance. A simulator with non-zero variance is non-deterministic but may be sufficient for some applications as long as variance is permissible, i.e. \textit{within tolerance}. Therefore, \textit{tolerance} is the acceptable degree of variability between repeated simulations. When the simulation output is within tolerance, coverage results are stable and, when a test fails, debugging can rely on the test producing the same trace and outcome when repeated. This ensures that software bugs can be found and fixed efficiently, and that simulation results are trustworthy.

>>>>

% NEW TEXT
Determinism is a key requirement for simulation during AV development and testing, it ensures repeated runs have the same output and therefore have zero variance. A simulator with non-zero variance is non-deterministic but may be sufficient for some applications as long as variance is permissible, i.e. \textit{within tolerance}. Therefore, \textit{tolerance} is the acceptable degree of variability between repeated simulations. When the simulation output is within tolerance, coverage results are stable and, when a test fails, debugging can rely on the test producing the same trace and outcome when repeated. This ensures that software bugs can be found and fixed efficiently, and that simulation results are trustworthy.
